Back to Normal Transits for the Disintegrating Planet Candidate KIC 12557548 b

### 2018-04-13 ms.tex
added back in info on the reference stars.

%The discovery of K2-22b \citep{sanchis-ojedak2-22}, WD 1145+017 \citep{vanderburg2015wdDisintegrating}, KOI 2700 \citep{rappaport2014KOI2700} showed that other systems have similar light curves and that other disintegrating planet systems may be useful laboratories for understanding disintegrating planets.
%Multi-wavelength light curve measurements show that the dust particles can have wavelength-dependent transmission, as predicted from sub-micron dust particles \citep{bochinski2015evolving,sanchis-ojedak2-22}.

%Furthermore, there are perplexing systems that also display stochastic transit behavior but for which there are still no agreed-upon explanations: KIC 8462852 (ie. Boyajian's star) \citep{boyajian846}, RIK-210 \citep{david2017rik210} and PTFO 8-8695 \citep{vanEyken2012ptfTTauri}.
%KIC 8462852 may be a family of comets from one or more parent bodies that recently were broken apart.
%RIK-210 and PTFO 8-8695 are both in young systems ($\lesssim$ 10 and $\lesssim$3 Myr respectively) so they may are proto-planet candidates.
%RIK-210 may have accreting material that causes variable extinction while PTFO 8-8695's orbit may be precessing and causing variations in transit depth depending on its longitude.

%The underlying planet candidate \sha\ has not been detected directly, but several observational constraints have placed upper limits on its size and mass.
%High precision radial velocity measurements of the host star put an upper limit on the reflex motion due to the planet and constrains the mass to be $\lesssim 1.2 M_{\mathrm Jup}$ \citep{croll2014}.
%There is no detection of secondary eclipses of \sha\ with a 3$\sigma$ upper limit of $5 \times 10^{-5}$ in the Kepler bandpass, which means that for an albedo of 0.5, the radius of the planet must be smaller than 4600 km \citep{vanWerkhoven2014}.
%The timescale of the variability of the transits gives a mass lot rate of order $\sim M_\oplus/Gyr$, which would indicate a present-day mass of 0.014 $M_\oplus$ when using a radiative-hydrodynamic wind model \citep{perez-becker}.

@@

Subsequently, \citet{schlawin2016kic1255} observed 8 total transits of the system for 4 nights in 2013 and 4 nights in 2014 for the $r'$ band using the MORIS imager \citep{Gulbis2011} on SpeX/IRTF \citep{rayner03}.
\citet{schlawin2016kic1255} found that the transit depths were all weaker than $0.43\%$ and that the probably of this randomly occurring based on random behavior from Kepler statistics was around 0.2\%.
This was evidence that the observations occurred during weaker periods (as found in \citet{vanWerkhoven2014}'s 15 Kepler quarter analysis) or that the disintegration activity was falling off with time.
We performed follow-up $R$ band photometry of the \shStar\ system to explore the second hypothesis: that the disintegration activity decreases as function of time.

\section{Observations}
We observed \sha\ with the Mont4k imager on the 61-inch Kuiper observatory on UT dates 2016-06-12, 2016-06-14, 2016-07-12, 2016-07-14, 2016-07-16.
The nights were clear with the exception of a few passing clouds on 2016-07-14.
We also attempted photometry on 2016-06-10, but clouds prevented precision time series.

@@

Figure \ref{fig:allNightrefCorrect} shows the reference-corrected time series for \shStar\ for all 5 nights which were timed with transits.
We use the following planet transit ephemeris, using the flux minimum from Kepler data \citep{schlawin2016kic1255} and the orbital period from \citet{vanWerkhoven2014}.
\begin{equation}
T = T_0 + n P
\end{equation}
where $T_0 = 2454833.039$ BJD$_{TDB}$ and $P = 0.653 553 8 \pm 0.000 000 1$ days.

>>>>

The discovery of K2-22b \citep{sanchis-ojedak2-22}, WD 1145+017 \citep{vanderburg2015wdDisintegrating}, KOI 2700 \citep{rappaport2014KOI2700} showed that other systems have similar light curves and that other disintegrating planet systems may be useful laboratories for understanding disintegrating planets.
Multi-wavelength light curve measurements show that the dust particles can have wavelength-dependent transmission, as predicted from sub-micron dust particles \citep{bochinski2015evolving,sanchis-ojedak2-22}.

Furthermore, there are perplexing systems that also display stochastic transit behavior but for which there are still no agreed-upon explanations: KIC 8462852 (ie. Boyajian's star) \citep{boyajian846}, RIK-210 \citep{david2017rik210} and PTFO 8-8695 \citep{vanEyken2012ptfTTauri}.
KIC 8462852 may be a family of comets from one or more parent bodies that recently were broken apart.
RIK-210 and PTFO 8-8695 are both in young systems ($\lesssim$ 10 and $\lesssim$3 Myr respectively) so they may be proto-planet candidates.
RIK-210 may have accreting material that causes variable extinction while PTFO 8-8695's orbit may be precessing and causing variations in transit depth depending on its longitude.

The underlying planet candidate \sha\ has not been detected directly, but several observational constraints have placed upper limits on its size and mass.
High precision radial velocity measurements of the host star put an upper limit on the reflex motion due to the planet and constrains the mass to be $\lesssim 1.2 M_{\mathrm Jup}$ \citep{croll2014}.
There is no detection of secondary eclipses of \sha\ with a 3$\sigma$ upper limit of $5 \times 10^{-5}$ in the Kepler bandpass, which means that for an albedo of 0.5, the radius of the planet must be smaller than 4600 km \citep{vanWerkhoven2014}.
The timescale of the variability of the transits gives a mass lot rate of order $\sim M_\oplus/Gyr$, which would indicate a present-day mass of 0.014 $M_\oplus$ when using a radiative-hydrodynamic wind model \citep{perez-becker}.

@@

Subsequently, \citet{schlawin2016kic1255} observed 8 total transits of the system for 4 nights in 2013 and 4 nights in 2014 for the $r'$ band using the MORIS imager \citep{Gulbis2011} on SpeX/IRTF \citep{rayner03}.
\citet{schlawin2016kic1255} found that the optical transit depths were all weaker than $0.43\%$ and that the probably of this randomly occurring based on random behavior from Kepler statistics was around 0.2\%.
This was evidence that the observations occurred during weaker periods (as found in \citet{vanWerkhoven2014}'s 15 Kepler quarter analysis) or that the disintegration activity was falling off with time.
We performed follow-up $R$ band photometry of the \shStar\ system to explore the second hypothesis: that the disintegration activity decreases as function of time.

\begin{deluxetable}{lr}
\tablecaption{List of observations}\label{tab:photSummary}
\tablewidth{0pt}
\tablehead{
\colhead{Date} &
\colhead{Comment} \\
\colhead{UT} & \\
 }
\startdata
2016-06-10 & Clouds \\
2016-06-12 & Clear \\
2016-06-14 & Clear \\
2016-07-12 & Clear \\
2016-07-14 & Mostly clear \\
2016-07-16 & Clear \\
\enddata
\tablenotetext{}{Summary of observations and conditions in this work.}
\end{deluxetable}

\section{Observations}
We observed \sha\ with the Mont4k imager on the 61-inch Kuiper observatory on UT dates 2016-06-12, 2016-06-14, 2016-07-12, 2016-07-14, 2016-07-16.
The nights were clear with the exception of a few passing clouds on 2016-07-14.
We also attempted photometry on 2016-06-10, but clouds prevented precision time series.
Table \ref{tab:photSummary} shows a summary of our observations and the UT dates.

@@

For the photometric reduction, we used the \texttt{ccdproc} package to generate master flat field and bias files.
I combined with an average with a low threshold of 2$\sigma$ and a high threshold of 5$\sigma$.

\begin{figure}
\begin{centering}
\includegraphics[width=0.5\textwidth]{images/ut2016_07_14_clouds/figure_index_152.pdf}
\includegraphics[width=0.5\textwidth]{images/stamps_kic1255_UT2016_07_14.pdf}
\caption{Target (src) and reference stars (numbered) used on UT 2016-07-14.
The reference stars were chosen to have similar count levels as the source. 
}\label{fig:ut2016-07-14cloudImg}
\end{centering}
\end{figure}

All nights light curves are shown in Figure \ref{fig:allNightallStar}.
These are the same reference stars shown in Figure \ref{fig:ut2016-07-14cloudImg}.
The nights two nights in June, 2016 show greater overall stability than the ones in July, 2016.
I suspect that this can mostly be explained by moisture and clouds (such as the ones that caused huge drops in flux on UT2016-07-14.

\begin{figure*}
\begin{centering}
\includegraphics[width=0.9\textwidth]{images/all_kic1255_phot/all_kic1255_allstar.pdf}
\caption{Time series photometry for all stars and all nights nights.
The nights in July appear more strongly affected by cloud/and or seeing variations, whereas the two nights in June are stable to within a few percent.
All source radius, background start and background annulus end parameters were 9, 9 and 12 pixels respectively.}\label{fig:allNightallStar}
\end{centering}
\end{figure*}

Figure \ref{fig:allNightrefCorrect} shows the reference-corrected time series for \shStar\ for all 5 nights which were timed with transits.
We use the following planet transit ephemeris, using the flux minimum ``transit center'' from Kepler data \citep{schlawin2016kic1255} and the orbital period from \citet{vanWerkhoven2014}.
\begin{equation}
T = T_0 + n P
\end{equation}
where $T_0 = 2454833.039$ BJD$_{TDB}$ and $P = 0.653 553 8 \pm 0.000 000 1$ days.
